\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{enumitem}
\setlist[enumerate,1]{start=0}

\title{Bean Bag Toss (Cornhole)}
\author{Ritzenthaler Tournament Rules}

\begin{document}
\maketitle
\begin{enumerate}
\item \textbf{If both teams can agree on a set of rules prior to beginning the game - \textit{any} set of rules - then they may use those rules even if they violate these. If both teams cannot agree, the rules MUST fall back to these.}
\item The team that tosses first is chosen by coin toss or a game of Rock-Paper-Scissors (best of ONE). The teammate that tosses first will be chosen by the team that is NOT tossing first. That is, if Team A wins the coin toss against Team B, then after choosing which teammate is on which side, Team B will decide which side tosses first.
\item Tosses take place in staggered order, first the first team tosses, then the other and so on until all bags have been tossed.
\item After the first round of tossing, the team with the higher number of points tosses first. If there is a tie in points, the team that previously tossed first still tosses first.
\item When tossing, the player must not step beyond the front of the board on his or her side.
\item A bag that rests on the board is worth one point, while a bag that goes through the hole in the board is worth three points.
\item A bag that touches the ground at any point after being tossed is considered "dead" until the next round, and can neither score points nor cancel points. A bag that lands on the edge of the board is considered dead if and only if it doesn't stay on when the board is lifted.
\item An opponent's bag resting in the same place as your own will cancel your points in that area. This means that if Team A has two bags on the board and a bag in the hole, then Team B's bag in the hole reduces the score to
	\begin{itemize}
		\item Team A: +2
		\item Team B: +0
	\end{itemize}
If, however, Team B gets another bag in the hole, it does NOT cancel with Team A's points on the board. Thus, the score for this round becomes
	\begin{itemize}
		\item Team A: +2
		\item Team B: +3
	\end{itemize}
\item The game is over when one team REACHES 21 points. If a team would go over 21 points within a round of tossing, they STILL WIN and DO NOT lose any points etc. If two teams reach 21 points within the same round of tossing, the team that reaches the highest amount of points is the winner. If both teams reach the same number of points (being at least 21 points), the game will continue as normal until at the end of a round one team pulls ahead in points, thus becoming the victor.
\end{enumerate}
\end{document}
